---
title: "efg's R Notes:  EBImage:  Color Basics"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html) | [Color](Color.html)** 

*****

```{r}
library(EBImage)
```

## Color images have three color planes

The *sample-color.png* file is the [Two Macaws](http://r0k.us/graphics/kodak/kodim23.html) true color image from [Kodak](http://r0k.us/graphics/kodak/).

```{r}
macaws <- readImage(system.file("images", "sample-color.png", package="EBImage"))
str(macaws)
```

Color images have *colormode* = 2.

```{r, fig.width=4, fig.height=3}
display(macaws)
```


Split color image into separate red, green and blue color planes, which can be displayed as *Grayscale* images.

```{r, fig.width=8, fig.height=2.5}
par(mfrow=c(1,3))
redPlane   <- channel(macaws, "red")
greenPlane <- channel(macaws, "green")
bluePlane  <- channel(macaws, "blue")

display(redPlane)
display(greenPlane)
display(bluePlane)
```

```{r}
str(redPlane)
str(greenPlane)
str(bluePlane)
```

*Grayscale* images have *colormode* = 0.

The *colormode* of a color image can be set to *Grayscale* to also visualize the color planes.  Use *all=TRUE* to see all images in the stack.

```{r, fig.width=6, fig.height=4.5}
colorMode(macaws) <- Grayscale
str(macaws)
display(macaws, all=TRUE)
```

The stack of images can be indexed via the third dimension of the image array.  Index=1 is the red plane, Index=2 is the green plane, and Index=3 is the blue plane.

## Histograms of color planes

```{r}
hist(macaws[,,1])
grid()
mtext("Red color plane")
```

*hist(redPlane)* would create the same histogram as above.

```{r}
hist(macaws[,,2])
grid()
mtext("Green color plane")

hist(macaws[,,3])
grid()
mtext("Blue color plane")
```

## Display single color plane in RGB

Let's display the *macaws* image with its shades of red and the green and blue color planes set to zero.

```{r, fig.width=4, fig.height=3}
colorMode(macaws) <- Color  # restore from above

macawsRed <- macaws   # leave red plane unchanged
str(macawsRed)       

macawsRed[,,2] <- 0   # set green to 0
macawsRed[,,3] <- 0   # seg blue  to 0

display(macawsRed)
```

Similarly, the green and blue planes can be displayed:

```{r, fig.width=4, fig.height=3}
macawsGreen <- macaws   # leave green plane unchanged      
macawsGreen[,,1] <- 0   # set red   to 0
macawsGreen[,,3] <- 0   # seg blue  to 0
display(macawsGreen)

macawsBlue <- macaws   # leave blue plane unchanged      
macawsBlue[,,1] <- 0   # set red   to 0
macawsBlue[,,2] <- 0   # seg green to 0
display(macawsBlue)
```

Adding the light from the red, green and blue images above results in the [RGB color image](http://en.wikipedia.org/wiki/RGB_color_model).

## Rotate the RGB color planes

With a real-world image there is likely no reason to change the color planes, but such a manipulation might make sense to display synthetic data using false colors.

```{r, fig.width=4, fig.height=3}
macawsFalseColor <- macaws

macawsFalseColor[,,1] <- channel(macaws, "green")  # set red   plane to green plane 
macawsFalseColor[,,2] <- channel(macaws, "blue")   # set green plane to blue  plane
macawsFalseColor[,,3] <- channel(macaws, "red")    # set blue  plane to red   plane
display(macawsFalseColor)
```

*****

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  