---
title: "efg's R Notes:  EBImage:  Combining Images"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html)** 

*****

```{r}
library(EBImage)
```

*combine* merges images to create image sequences.

The function *combine* merges multi-dimensional arrays along the dimension depending on the color mode of image x, which is the first image specified. If x is a *Grayscale* image or an array, image objects are combined along the third dimension, whereas when x is a *Color* image they are combined along the forth dimension, leaving room on the third dimension for color channels.  [from **?combine** help]

## Combination of color images

### Image, Flip, Flop
```{r, fig.width=6}
img <- readImage(system.file("images", "sample-color.png", package="EBImage"))[257:768,,]
x <- combine(img, flip(img), flop(img))
display(x, all=TRUE)
```

## Blurred images

### Sequence 
```{r, fig.width=6}
x <- resize(img, 128, 128)
xt <- list()
for (t in seq(0.1, 5, len=9)) xt=c(xt, list(gblur(x, s=t)))
xt <- combine(xt)
display(xt, title='Blurred images', all=TRUE)
```

*****

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  