---
title: "efg's R Notes:  EBImage:  Basic Features"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html) | [Features](Features.html)**

**Basic | [Haralick](Features-Haralick.html) | [Moment](Features-Moment.html) | [Shape](Features-Shape.html)** 

*****

The function *computeFeatures.basic* computes spatial-independent statistics on pixel intensities: 

* b.mean: mean intensity 
* b.sd: standard deviation intensity 
* b.mad: median absolute deviation (mad) intensity 
* b.q\*: quantile intensity 

All basic features have a prefix "b.".  

Intensity values range from 0.0 to 1.0. 

```{r}
library(EBImage)
```

```
computeFeatures.basic(x, ref, properties=FALSE, basic.quantiles=c(0.01, 0.05, 0.5, 0.95, 0.99), xs, ...)
```

## List properties of basic features
```{r, comment=NA}
feature.properties <- computeFeatures.basic(properties=TRUE)
feature.properties
```

## Load and segment nucleus

```{r, fig.width=4, fig.height=2}
par(mfrow=c(1,2))
y <- readImage(system.file("images", "nuclei.tif", package="EBImage"))[,,1]
x <- thresh(y, 10, 10, 0.05)
x <- opening(x, makeBrush(5, shape='disc'))
x <- bwlabel(x)

display(y, title="Cell nuclei")
display(x, title="Segmented nuclei")
```

## Compute basic features

```{r, fig.width=8, comment=NA}
basicFeatures <- computeFeatures.basic(x, y)
str(basicFeatures)
options(digits=4)
basicFeatures
```

## Correlations of basic features

```{r}
correlationMatrix <- cor(basicFeatures)
correlationMatrix
```

## Heatmaps of correlation matrix

### Color-coded display of correlation matrix

```{r, message=FALSE}
library(gplots)         # heatmap.2
library(RColorBrewer)   # brewer.pal
```

```{r, fig.width=6, fig.height=6}
heatmap.2(correlationMatrix, dendrogram="none", Rowv=FALSE, symm=TRUE,
          cellnote=format(round(correlationMatrix,2)),
          main="Basic Features",
          scale="none", col=brewer.pal(11,"RdBu"), margins=c(9,9), trace="none")
```

### Dendrograms show relationships in correlation matrix

```{r, fig.width=6, fig.height=6, warning=NA}
heatmap.2(correlationMatrix, key=FALSE,
          cellnote=format(round(correlationMatrix,2)),
          main="Basic Features",
          scale="none", col=brewer.pal(11,"RdBu"), margins=c(9,9), trace="none")
```

A [diverging palette](../../package/RColorBrewer/index.html) from RColorBrewer is used for the heatmaps since correlations can range from -1 to +1. In the *RdBu* pallete, red is low and blue is high.

*****

```{r}
packageVersion("EBImage")
packageVersion("gplots")
packageVersion("RColorBrewer")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  