---
title: "efg's R Notes:  EBImage:  Moment Features"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html) | [Features](Features.html)**

**[Basic](Features-Basic.html) | [Haralick](Features-Haralick.html) | Moment | [Shape](Features-Shape.html)** 

*****

The function computeFeatures.moment computes features related to object image moments, which can be computed with or without reference intensities: 

* m.cx: center of mass x [pixels] 
* m.cy: center of mass y [pixels] 
* m.majoraxis: elliptical fit major axis [pixels] 
* m.eccentricity: elliptical [eccentricity](http://en.wikipedia.org/wiki/Eccentricity_(mathematics)) defined by $\sqrt{1 - \frac {MinorAxis^2}{MajorAxis^2}}$. Circle eccentricity is 0 and straight line eccentricity is 1. 
* m.theta: object angle [radians] 

All moment features have a prefix "m.".  

```{r}
library(EBImage)
```

```
computeFeatures.moment(x, ref, properties=FALSE, xs, ...)
```

## List properties of moment features
```{r, comment=NA}
moment.properties <- computeFeatures.moment(properties=TRUE)
moment.properties
```

## Load and segment nucleus

```{r, fig.width=4, fig.height=2}
par(mfrow=c(1,2))
y <- readImage(system.file("images", "nuclei.tif", package="EBImage"))[,,1]
x <- thresh(y, 10, 10, 0.05)
x <- opening(x, makeBrush(5, shape='disc'))
x <- bwlabel(x)

display(y, title="Cell nuclei")
display(x, title="Segmented nuclei")
```

## Compute moment features

```{r, fig.width=8, comment=NA}
momentFeatures <- computeFeatures.moment(x, y)
str(momentFeatures)
options(digits=4)
momentFeatures
```

## Correlations of moment features

```{r}
correlationMatrix <- cor(momentFeatures)
correlationMatrix
```

*****

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  