---
title: "efg's R Notes:  EBImage:  Haralick Features"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html) | [Features](Features.html)**

**[Basic](Features-Basic.html) | Haralick | [Moment](Features-Moment.html) | [Shape](Features-Shape.html)** 

**[Haralick Textural Features Details](Haralick-Textural-Features.html)**

*****

The function *computeFeatures.haralick* computes features that quantify pixel texture. Features are named according to Haralick's original paper. See **[Haralick Textural Features Details](Haralick-Textural-Features.html)** for details about the 26 features. 

All Haralick features have a prefix "h.".  

```{r}
library(EBImage)
```

```
computeFeatures.haralick(x, ref , properties=FALSE, haralick.nbins=32, haralick.scales=c(1, 2), xs, ...)
```

## List properties of Haralick features
```{r, comment=NA}
feature.properties <- computeFeatures.haralick(properties=TRUE)
feature.properties
```

## Load and segment nucleus

```{r, fig.width=4, fig.height=2}
par(mfrow=c(1,2))
y <- readImage(system.file("images", "nuclei.tif", package="EBImage"))[,,1]
x <- thresh(y, 10, 10, 0.05)
x <- opening(x, makeBrush(5, shape='disc'))
x <- bwlabel(x)

display(y, title="Cell nuclei")
display(x, title="Segmented nuclei")
```

## Compute Haralick features

```{r, fig.width=8, comment=NA}
haralickFeatures <- computeFeatures.haralick(x, y)
str(haralickFeatures)
options(digits=4, width=100)
haralickFeatures
```

## Correlations of Haralick features

```{r}
correlationMatrix <- cor(haralickFeatures)
correlationMatrix
```

*****

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  