---
title: "efg's R Notes:  EBImage:  Shape Features"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html) | [Features](Features.html)**

**[Basic](Features-Basic.html) | [Haralick](Features-Haralick.html) | [Moment](Features-Moment.html) | Shape** 

*****

The function *computeFeatures.shape* computes features that quantify object shape: 

* s.area: area size [pixels^2] 
* s.perimeter: perimeter [pixels] 
* s.radius.mean: mean radius [pixels] 
* s.radius.sd: standard deviation of the mean radius [pixels] 
* s.radius.max: max radius [pixels] 
* s.radius.min: min radius [pixels] 

All shape features have a prefix "s.".  


```{r}
library(EBImage)
```

```
computeFeatures.shape(x, properties=FALSE, xs, ...)
```

## List properties of shape features
```{r, comment=NA}
feature.properties <- computeFeatures.shape(properties=TRUE)
feature.properties
```

## Load and segment nucleus

```{r, fig.width=4, fig.height=2}
par(mfrow=c(1,2))
y <- readImage(system.file("images", "nuclei.tif", package="EBImage"))[,,1]
x <- thresh(y, 10, 10, 0.05)
x <- opening(x, makeBrush(5, shape='disc'))
x <- bwlabel(x)

display(y, title="Cell nuclei")
display(x, title="Segmented nuclei")
```

## Compute shape features

```{r, fig.width=8, comment=NA}
shapeFeatures <- computeFeatures.shape(x)
str(shapeFeatures)
options(digits=4, width=100)
shapeFeatures
```

## Correlations of shape features

```{r}
correlationMatrix <- cor(shapeFeatures)
correlationMatrix
```

## Heatmaps of correlation matrix

### Color-coded display of correlation matrix

```{r, message=FALSE}
library(gplots)         # heatmap.2
library(RColorBrewer)   # brewer.pal
```

```{r, fig.width=6, fig.height=6}
heatmap.2(correlationMatrix, dendrogram="none", Rowv=FALSE, symm=TRUE,
          cellnote=format(round(correlationMatrix,2)),
          main="Shape Features",
          scale="none", col=brewer.pal(11,"RdBu"), margins=c(9,9), trace="none")
```

### Dendrograms show relationships in correlation matrix

```{r, fig.width=6, fig.height=6, warning=NA}
heatmap.2(correlationMatrix, key=FALSE,
          cellnote=format(round(correlationMatrix,2)),
          main="Shape Features",
          scale="none", col=brewer.pal(11,"RdBu"), margins=c(9,9), trace="none")
```

A [diverging palette](../../package/RColorBrewer/index.html) from RColorBrewer is used for the heatmaps since correlations can range from -1 to +1. In the *RdBu* pallete, red is low and blue is high.

*****

```{r}
packageVersion("EBImage")
packageVersion("gplots")
packageVersion("RColorBrewer")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  