---
title: 'EBImage:  Filters and Filtering'
author: "Earl F Glynn"
output: html_document
---

```{r}
library(EBImage)
```
# Filters

## filter2:  2D Convolution Filter 

Filters an image using the fast 2D FFT convolution product. 

```{r}
x <- readImage(system.file("images", "sample-color.png", package="EBImage"))
display(x, title='Sample')
```

## Low-pass disc-shaped filter
```{r}
f <- makeBrush(21, shape='disc', step=FALSE)
display(f, title='Disc filter')
f <- f/sum(f)
y <- filter2(x, f)
display(y, title='Filtered image')
```

## High-pass Laplacian filter
```{r}
la <- matrix(1, nc=3, nr=3)
la[2,2] <- -8
la
y <- filter2(x, la)
display(y, title='Filtered image')
```

**The above image is not correct.  It will be fixed in the next version.**

## gblur:  Low-pass Gaussian filter

Filters an image with a low-pass Gaussian filter. 

```{r}
x <- readImage(system.file("images", "sample.png", package="EBImage"))
display(x)

y <- gblur(x, sigma=8)
display(y, title='gblur(x, sigma=8)')
```

## medianFilter:  2D constant time median filtering

Filters a 16-bit image using Perreault's modern constant time median filtering algorithm.

Median filtering is useful as a smoothing technique, e.g. in the removal of speckling noise. 

```{r}
x <- readImage(system.file("images", "nuclei.tif", package="EBImage"))
display(x, title='Nuclei', all=TRUE)
y <- medianFilter(x, 5)  
display(y, title='Filtered nuclei', all=TRUE)
```


```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  