---
title: "efg's R Notes:  EBImage:  Image Display and I/O"
output: html_document
---

**[RNotes](../../index.html) | [EBImage](index.html)** 

*****

```{r}
library(EBImage)
```

# Image Display

## Display a single image

```{r, fig.width=4, fig.height=3}
x <- readImage(system.file("images", "sample-color.png", package="EBImage"))[257:768,,]
display(x, "Sample")
```

## Display a thresholded sequence ...

```{r}
y <- readImage(system.file("images", "sample.png", package="EBImage"))
yt <- list()
for (t in seq(0.1, 5, len=9)) yt=c(yt, list(gblur(y, s=t)))
yt <- combine(yt)
```

## ... using the browser viewer ...

```{r, fig.width=4, fig.height=3}
display(yt, "Blurred images")
display(yt, "Blurred images", all=TRUE)
```

## ... or using R's build-in raster functions

```{r, fig.width=4, fig.height=3}
display(resize(yt, 256, 256), method = "raster", all = TRUE)
```

## Display the last frame 

```{r, fig.width=4, fig.height=3}
display(yt, method = "raster", frame = numberOfFrames(yt, type = "render"))
```

# Image I/O

## Read and display an image

```{r, fig.width=4, fig.height=3}
f <- system.file("images", "sample-color.png", package="EBImage")
x <- readImage(f)
display(x)
```

## Read and display a multi-frame TIFF

```{r}
y <- readImage(system.file("images", "nuclei.tif", package="EBImage"))
display(y)
display(y, all=TRUE)
```

## Read an image directly from a remote location by specifying its URL

```{r, fig.width=4, fig.height=3}
try({
  im <- readImage("http://www-huber.embl.de/EBImage/ExampleImages/berlin.tif")
  display(im, title = "Berlin Impressions", all=TRUE)
})
```

## Convert a PNG file into JPEG

```{r, fig.width=4, fig.height=3}
tempfile <- tempfile("", , ".jpeg")
writeImage(x, tempfile, quality = 85)
cat("Converted '", f, "' into '", tempfile, "'.\n", sep="")
```

## Save a frame sequence

```{r}
files <- writeImage(y, tempfile("", , ".jpeg"), quality = 85)
cat("Files created: ", files, sep="\n")
```

*****

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  