---
title: 'EBImage:  Morphological Operations'
author: "Earl F Glynn"
output: html_document
---

```{r}
library(EBImage)
```

# Morphological Operations

- blackTopHatGreyScale
- closing
- closingGreyScale
- dilate
- dilateGreyScale
- erode
- erodeGreyScale
- makeBrush
- opening
- openingGreyScale
- selfcomplementaryTopHatGreyScale
- whiteTopHatGreyScale   

## Example

```{r, fig.width=8, fig.height=2}
par(mfrow=c(1,5))
x <- readImage(system.file("images", "shapes.png", package="EBImage"))
kern <- makeBrush(5, shape='diamond')  
  
display(x)
display(kern, title='Structuring element')
display(erode(x, kern), title='Erosion of x')
display(dilate(x, kern), title='Dilatation of x')
```

## makeBrush
```{r, fig.width=8, fig.height=2.5}
par(mfrow=c(1,3))
display(makeBrush(99, shape='diamond'))
display(makeBrush(99, shape='disc', step=FALSE))
display(2000*makeBrush(99, shape='Gaussian', sigma=10))
```

## Example 2

From *[Introduction to EBImage](http://www.bioconductor.org/packages/release/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.pdf)* by Andrzej Oles et al, Dec. 3, 2014.

Binary images are images where the pixels of value 0 constitute the background and the other ones constitute the foreground. These images are subject to several non-linear mathematical operators called morphological operators, able to erode and dilate an image.

```{r fig.width=4, fig.height=1.5, fig.cap="eierode, eidilat"}
ei <- readImage(system.file('images', 'shapes.png', package='EBImage'))
ei <- ei[110:512,1:130]
display(ei, title="Figure 10: ei")

kern <- makeBrush(5, shape='diamond')
eierode <- erode(ei, kern)
display(eierode, title="eierode")

eidilat <- dilate(ei, kern)
display(eidilat, title="eidilat")
```

```{r}
packageVersion("EBImage")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`  