---
title: "efg's R Notes:  minpack.lm:  Non-Linear Curve Fit"
output: html_document
---

*****

```{r}
library(minpack.lm)
```


## Non-Linear Curve Fit Example from nls.lm package

Use Levenberg-Marquardt algorithm for non-linear curve fitting.

### Background info

* [Levenberg-Marquardt algorithm](http://en.wikipedia.org/wiki/Levenberg%E2%80%93Marquardt_algorithm)
* [R package minpack.lm](http://cran.r-project.org/web/packages/minpack.lm/minpack.lm.pdf)
* [MinPack info](http://www.netlib.org/minpack/ex/file06)


### Created simulated data with noise

Function to simulate data 
```{r}
f <- function(T, tau, N0, a, f0) 
{
  expr <- expression(N0 * exp(-T/tau) * (1 + a*cos(f0*T)))
  eval(expr)
}
```

Values over which to simulate data: 500 intervals between 0 and 8 
```{r}
T <- seq(0, 8, length=501)
```

Parameter values underlying simulated data  
```{r}
p <- c(tau = 2.2, N0 = 1000, a = 0.25, f0 = 8)
```

Define vector with simulated data to fit

```{r}
Ndet <- do.call("f", c(list(T = T), as.list(p)))
```

Add noise.  Set random number seed so example is reproducible.

```{r}
set.seed(17)
N <- Ndet +  rnorm(length(Ndet), mean=Ndet, sd=.01*max(Ndet))
head(N)
```

## Non-linear curve fit

### Helper function for an analytical gradient. 

Function *D* computes derivatives with respective to named parameter.

$$ N_0 exp(-T/tau) (1 + a\cos(f0 T)) $$

See info [about Hessian/Jacobian matrix](http://mathworld.wolfram.com/Hessian.html).

```{r}
j <- function(T, tau, N0, a, f0) 
{
  expr <- expression(N0*exp(-T/tau)*(1 + a*cos(f0*T)))
  c(eval(D(expr, "tau")), 
    eval(D(expr, "N0" )),
    eval(D(expr, "a"  )), 
    eval(D(expr, "f0" )))
}
```

### Define a residual function 

```{r}
fcn <- function(p, T, N, fcall, jcall)
    (N - do.call("fcall", c(list(T = T), as.list(p))))
```

### Define analytical expression for the gradient

```{r}
fcn.jac <- function(p, T, N, fcall, jcall) 
{
  -do.call("jcall", c(list(T = T), as.list(p)))
}  
```

### Initial guess starting values 
```{r}
guess <- c(tau = 2.2, N0 = 1500, a = 0.25, f0 = 10)
```

### Non-linear curve fit
```{r}
out <- nls.lm(par = guess, fn = fcn, jac = fcn.jac,
              fcall = f, jcall = j,
              T = T, N = N, control = nls.lm.control(nprint=1))
```

### get the fitted values 
```{r}
N1 <- do.call("f", c(list(T = T), out$par))  
```

### Plots

Plot the original data with fitted solution, along with residuals.

```{r datatofit, fig.width=6, fig.height=6}
plot(T, N, cex = 0.5, main="Simulated Data to Fit")
grid()
lines(T, N1, col="blue", lwd=2)   # Fitted solution
```

Add a plot of the log residual sum of squares as it is made to decrease each iteration; note that the RSS at the starting parameter values is also stored

```{r residuals, fig.width=6, fig.height=6}
plot(1:(out$niter+1), log(out$rsstrace), type="b",
     main="log residual sum of squares vs. iteration number",
     xlab="iteration", 
     ylab="log residual sum of squares", pch=21) 
grid()
```

### Information regarding standard errors
```{r, comment=NA}
summary(out) 
```

*****
```{r}
packageVersion("minpack.lm")
```

*efg*

`r format(Sys.time(), "%Y-%m-%d %H%M")`

