---
title: 'efg''s R Notes:  waveslim:  dwt.2d'
output: html_document
---

```{r, message=FALSE}
library(waveslim)
```

## dwt.2d

Perform a separable two-dimensional discrete wavelet transform (DWT) on a matrix of dyadic dimensions (powers of 2). 

### Xbox image

```{r}
data(xbox)
xbox.dwt <- dwt.2d(xbox, "haar", 3)
par(mfrow=c(1,1), pty="s")
plot.dwt.2d(xbox.dwt)
par(mfrow=c(2,2), pty="s")
image(1:dim(xbox)[1], 1:dim(xbox)[2], xbox, xlab="", ylab="",
      main="Original Image")
image(1:dim(xbox)[1], 1:dim(xbox)[2], idwt.2d(xbox.dwt), xlab="", ylab="",
      main="Wavelet Reconstruction")
image(1:dim(xbox)[1], 1:dim(xbox)[2], xbox - idwt.2d(xbox.dwt),
      xlab="", ylab="", main="Difference")
```

### Ingrid Daubechies image

The [Daubechies wavelets](http://en.wikipedia.org/wiki/Daubechies_wavelet) are based on the work of Ingrid Daubechies.

```{r, fig.width=4}
data(dau)
dim(dau)
hist(dau)
par(mfrow=c(1,1), pty="s")
image(dau, col=rainbow(128))
sum(dau^2)
dau.dwt <- dwt.2d(dau, "d4", 3)
plot.dwt.2d(dau.dwt)
sum(plot.dwt.2d(dau.dwt, plot=FALSE)^2)
```
Explanation of above image:  [How to apply DWT (Discrete Wavelet Transform) to Image?](http://imagelpcmatlab.blogspot.com/2013/12/how-to-apply-dwt-discrete-wavelet.html)

**References**

* Stephane Mallat.  *[A Wavelet Tour of Signal Processing](https://www.ceremade.dauphine.fr/~peyre/wavelet-tour/)*.  Academic Press, 2008.

* Martin Vetterli and Jelena Kovacevic.  *[Wavelets and Subband Coding](http://waveletsandsubbandcoding.org/Repository/VetterliKovacevic95_Manuscript.pdf)*, Prentice Hall 1995.

* Ramazan Gen?ay, Faruk Sel?uk, and Brandon Whitcher. *[An Introduction to Wavelets and Other Filtering Methods in Finance and Economics](http://wwwf.imperial.ac.uk/~bwhitche/book/software.html)*.  Academic Press, 2001.

*****

```{r}
packageVersion("waveslim")
```       

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`                   
                                                                                    