---
title: 'efg''s R Notes:  waveslim:  wavelet functions'
output: html_document
---

```{r, message=FALSE}
library(waveslim)
```

## wave.filter

Convert name of wavelet filter to filter coefficients. 

There are holes in the documentation of what the wavelet names mean:
   
|Name |Wavelet       |
|-----|--------------|
|bl14 |Best Localized|
|bl20 |Best Localized|
|bs3.1|Best Localized|
|d4   |Daubechies    |
|d6   |Daubechies    |
|d8   |Daubechies    |
|d16  |Daubechies    |
|fk4  |              |
|fk6  |              |
|fk8  |              |
|fk14 |              |
|fk22 |              |
|haar |Haar          |
|la8  |Least Asymmetric|
|la16 |Least Asymmetric|
|la20 |Least Asymmetric|
|mb4  |              |
|mb8  |              |
|mb16 |              |
|mb24 |              |
|w4   |              |

```{r}
d4  <- wave.filter("d8")
str(d4)
plot(d4$lpf, main="d8")
grid()
plot(d4$hpf, main="d8")
grid()
```


*****

```{r}
packageVersion("waveslim")
```       

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")`      
