---
title: "efg's R Notes:  RColorBrewer Package"
output: html_document
---

**[RNotes](../../index.html)**  

*****

# ColorBrewer Palettes

```{r}
library(RColorBrewer)
```

## Sequential palettes

Sequential palettes are suited to ordered data that progress from low to high. Lightness steps dominate the look of these schemes, with light colors for low data values to dark colors for high data values. 

All the sequential palettes are available in variations from 3 different values up to 9 different values. 
 
```{r, fig.height=4}
par(mar=c(1,5,1,1))
display.brewer.all(type="seq")
brewer.pal.info[brewer.pal.info$category == "seq",]

brewer.pal.info["Blues",]
brewer.pal.info["Blues",]$maxcolors
```

```{r, fig.height=2}
par(mar=c(1,1,1,1))
N <- 7
mypalette <- brewer.pal(N,"Blues")
image(1:7,1,as.matrix(1:N),col=mypalette,xlab="Blues (sequential)",
       ylab="",xaxt="n",yaxt="n",bty="n")
```
    
```{r, fig.height=2}
par(mar=c(1,1,1,1))
display.brewer.pal(N,"Blues")
```
    
## Diverging Palettes

Diverging palettes put equal emphasis on mid-range critical values and extremes at both ends of the data range. The critical class or break in the middle of the legend is emphasized with light colors and low and high extremes are emphasized with dark colors that have contrasting hues. 

All the diverging palettes are available in variations from 3 different values up to 11 different values. 

```{r, fig.height=4}
par(mar=c(1,5,1,1))
display.brewer.all(type="div")
brewer.pal.info[brewer.pal.info$category == "div",]

display.brewer.all(n=5,type="div",exact.n=TRUE)
```

```{r, fig.height=2}
par(mar=c(1,1,1,1))
display.brewer.pal(7,"BrBG")
```

## Qualitative Palettes

Qualitative palettes do not imply magnitude differences between legend classes, and hues are used to create the primary visual differences between classes. Qualitative schemes are best suited to representing nominal or categorical data. 

For qualitative palettes, the lowest number of distinct values available always is 3, but the largest number is different for different palettes. 

```{r, fig.height=4}
par(mar=c(1,5,1,1))
display.brewer.all(type="qual") 
brewer.pal.info[brewer.pal.info$category == "qual",]
```

```{r, fig.height=2}
par(mar=c(1,1,1,1))
display.brewer.pal(7,"Accent")
```

## Color-Blind Friendly Palettes

```{r, fig.height=6}
par(mar=c(1,5,1,1))
display.brewer.all(colorblindFriendly=TRUE)
brewer.pal.info[brewer.pal.info$colorblind,]
```


## All palettes simultanoeusly

```{r, fig.height=6}
par(mar=c(1,5,1,1))
display.brewer.all(n=10, exact.n=FALSE)

display.brewer.all(n=10)

display.brewer.all()

brewer.pal.info
```


*****

## ColorBrewer Info

ColorBrewer is Copyright (c) 2002 Cynthia Brewer, Mark Harrower, and The Pennsylvania State University. All rights reserved.

The ColorBrewer palettes have been included in this R package with permission of the copyright holder. 

View the [ColorBrewer web site](http://colorbrewer2.org/).
 
*****

```{r}
packageVersion("RColorBrewer")
```

*efg*  
`r format(Sys.time(), "%Y-%m-%d  %H%M")` 