---
title: "efg's R Notes:  Boruta Package"
output: html_document
---

**[RNotes](../../index.html)**     

Miron B. Kursa, Witold R. Rudnicki,  [Feature Selection with the Boruta Package](http://www.jstatsoft.org/v36/i11/), *Journal of Statistical Software*, Vol. 36, Issue 11, Sept 2010.

*****   

`r format(Sys.time(), "%Y-%m-%d %H%M")`

```{r, comment=NA}
library(Boruta)
```

## Iris dataset

```{r, comment=NA}
dim(iris)
head(iris)
```

### Takes some time, so be patient
```{r, comment=NA}
Bor.iris <- Boruta(Species~.,data=iris,doTrace=2)
print(Bor.iris);
print(getSelectedAttributes(Bor.iris))
```

### Add some nonsense attributes to iris dataset by shuffling original attributes

```{r, comment=NA}
set.seed(777);
iris.extended <- data.frame(iris,apply(iris[,-5],2,sample))
names(iris.extended)[6:9] <- paste("Nonsense",1:4,sep="")

dim(iris.extended)
head(iris.extended)
```

### Run Boruta on this data

```{r, comment=NA}
Boruta.iris.extended <- Boruta(Species~., data=iris.extended, doTrace=2)
```

### Nonsense attributes should be rejected
```{r, comment=NA}
print(Boruta.iris.extended)
```

### Boruta using rFerns' importance
```{r, comment=NA}
Boruta.ferns.irisE <- Boruta(Species~., data=iris.extended, getImp=getImpFerns)
print(Boruta.ferns.irisE)
```

## Ozone data from mlbench package

```{r, comment=NA}
library(mlbench)
data(Ozone)
ozo <- na.omit(Ozone)
dim(ozo)
head(ozo)
```

### Takes some time, so be patient

```{r, comment=NA}
Bor.ozo <- Boruta(V4~., data=ozo, doTrace=2)
cat('Random forest run on all attributes:\n')

print(randomForest(V4~., data=ozo))
cat('Random forest run only on confirmed attributes:\n')

print(randomForest(ozo[,getSelectedAttributes(Bor.ozo)],ozo$V4))
```

## Boruta on the HouseVotes84 data from mlbench

```{r, comment=NA}
library(mlbench)
data(HouseVotes84)

hvo <- na.omit(HouseVotes84)
dim(hvo)
head(hvo)
```

### Takes some time, so be patient

```{r, comment=NA}
Bor.hvo <- Boruta(Class~., data=hvo, doTrace=2)
print(Bor.hvo)
plot(Bor.hvo, las=2, cex.axis=0.75)
```

## Boruta on the Sonar data from mlbench

```{r, comment=NA}
library(mlbench)
data(Sonar)
```

### Takes some time, so be patient

```{r, comment=NA}
Bor.son <- Boruta(Class~.,data=Sonar,doTrace=2)
print(Bor.son)
plotImpHistory(Bor.son)

stats <- attStats(Bor.son)
print(stats)
plot(normHits~meanZ, col=stats$decision, data=stats)
```

### Shows important bands

```{r, comment=NA, plot.width=7}
plot(Bor.son,sort=FALSE, las=2, cex.axis=0.75)
```

*****  

```{r}
packageVersion("Boruta")
```

*efg*

`r format(Sys.time(), "%Y-%m-%d %H%M")`
                                                     
